BEX3012 Project Analysis

### 2017-04-21 Internship/BEX3012ProjectReport.Rmd
Emotion Distribution Plotting

#Read in data files
ME <- read_csv("data/MicrosoftEmotions.csv")
SB <- read_csv("data/SkybiometryEmotions.csv")
GE <- read_csv("data/GoogleFacesEmotions.csv")

EmotionSoftwareSpecs<-read_csv("Figures/EmotionSoftwareSpecifications.csv")

@@

```{r}

#Create normalised GE values
Conf <- function(Emot){
ifelse(Emot=="VERY_UNLIKELY", 10,  
        ifelse(Emot == "UNLIKELY", 30, 
                ifelse(Emot == "POSSIBLE", 50, 
                ifelse(Emot == "LIKELY", 70, 
                ifelse(Emot == "VERY_LIKELY", 90, NA)))))
}

@@

```{r VisualSet, echo=F, fig.cap = "Here are six examples of Faces in the image set after extracting faces from the full broadcast video stills. \\label{tab:VisualSet}"}

@@

    p <- ggplot(data.frame(x=c(0,350), y=c(0,350)), aes(x,y))+
      theme_classic() + xlab("") + ylab("") + 
      annotation_custom(rasterGrob(img)) +
      coord_cartesian(xlim=c(0, 350), ylim=c(0,400))

@@

f1 <- plotFaces("face-1635-1-Go.png")
f2 <- plotFaces("face-1128-1-Go.png")
f3 <- plotFaces("face-1746-1-Go.png")
f4 <- plotFaces("face-626-1-Go.png")
f5 <- plotFaces("face-450-1-Go.png")
f6 <- plotFaces("face-816-1-Go.png")

grid.arrange(f1, f2, f3, f4, f5, f6,nrow=2)

@@

We will consider three Emotion Recognition software.

@@

As can be seen above, a noticeable difference between the three is the amount of times the API can be called. Skybiometry had the largest imposition on Bath Processing as it only allowed 100 API calls to be processed per hour. Microsoft also had a limit imposed, but this allowed for much more to be processed with the possibility of 1200 images to be processed within an hour, after accounting for the wait time between each group of 20.
Google Vision's API batch processing limit had a minimal effect.

The range of outputs from the software is displayed as Google provides likelihoods of an emotion occurring on a particular face. Microsoft and Skybiometry provide outputs on the same emotions^[Based on Paul Ekmans emotion theories]. However the values that they provide differ as Microsoft provide Proportions whereas Skybiometry results in a Confidence of the emotion occurring in the specified face.

@@

```{r MEexample, echo=F, message=F, fig.cap = "\\label{tab:MEexample}"}
library(dplyr)
MEexample <- ME %>% subset(FileName=="face-1745-1-Go.png")

>>>>

#Read in data files
ME <- read_csv("data/MicrosoftEmotions.csv")
SB <- read_csv("data/SkybiometryEmotions.csv")
GE <- read_csv("data/GoogleFacesEmotions.csv")
DE <- read_csv("data/DominantEmotion.csv")

EmotionSoftwareSpecs <- read_csv("Figures/EmotionSoftwareSpecifications.csv")

@@

```{r}
#Create normalised GE values
Conf <- function(Emot){
ifelse(Emot=="VERY_UNLIKELY", 10,  
        ifelse(Emot == "UNLIKELY", 30, 
                ifelse(Emot == "POSSIBLE", 50, 
                ifelse(Emot == "LIKELY", 70, 
                ifelse(Emot == "VERY_LIKELY", 90, NA)))))
}

@@

```{r VisualSet, echo=F, fig.cap = "Three Faces in the image set, after extracting faces from the full broadcast video stills, and the dominant emotion each software recognised for them. \\label{fig:VisualSet}"}

@@

    p <- ggplot(data.frame(x=c(0,350), y=c(0,350)), aes(x,y))+
      theme_void() + 
      annotation_custom(rasterGrob(img)) +
      coord_cartesian(xlim=c(0, 350), ylim=c(0,400))

@@

TableEmotions <- function(imgList){
  for(i in imgList){

   d <- DE %>% filter(FileName== i)

  dl <- d %>% 
  select(Skybiometry = SEmotion, Microsoft = MEmotion, Google = GEmotion) %>%
    gather(key = Software, value = Emotion, Microsoft, Skybiometry, Google)

  t <- tableGrob(dl, theme = ttheme_minimal(), rows = c("", "", ""))

  } 
  return(t)
  }

#Faces 
f1 <- "face-1635-1-Go.png"
f2 <- "face-1128-1-Go.png"
f3 <- "face-1746-1-Go.png"

i1 <- plotFaces(f1)
i2 <- plotFaces(f2)
i3 <- plotFaces(f3)

# Tables of their resulting emotion value
t1 <- TableEmotions(f1)
t2 <- TableEmotions(f2)
t3 <- TableEmotions(f3)

#f4 <- "face-626-1-Go.png"
#f5 <- "face-450-1-Go.png"
#f6 <- "face-816-1-Go.png"

grid.arrange(i1, i2, i3, t1, t2, t3, nrow=2)

@@

We have considered three Emotion Recognition APIS.
They were chosen for their accessibility and online reviews, as these are well recognised options for Facial recongition currently available.

@@

As can be seen above, a noticeable difference between the three is the amount of times the API can be called within a given time frame. Skybiometry had the largest imposition on Call Limits as it only allowed 100 API calls to be processed per hour. Microsoft also had a limit imposed, but this allowed for much more to be processed with the possibility of 1200 images to be processed within one hour, after accounting for the wait time between each group of 20.
Google Vision's API call limit had a minimal effect for our purposes.

The number of emotions shown in the results were not congruent. These differences required pre processing to find the most comparable results for analysis.
Microsoft provided the most emotion options, contempt being the addition that was not provided by Skybiometry. Google provided the least, only giving the options for four different emotions.

The outputs from the APIs were very different. Google provides likelihoods of an emotion occurring on a particular face in categorical options ranging from Very Unlikely to Very Likely. Microsoft provide Proportions, ranging between 0 and , whereas Skybiometry results in a Confidence of the emotion occurring in the specified face in values from 0 to 100.

@@

```{r MEexample, echo=F, message=F, fig.cap = "\\label{tab:MEexample}"}

MEexample <- ME %>% subset(FileName=="face-1745-1-Go.png")

### 2017-04-21 Internship/EmotionsAnalysis.Rmd
Emotion Distribution Plotting

```{r cache=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = F, warning = F, cache=T)

@@

```{r}
#EmoM <-read_csv("data/EmotionsMerged.csv")
ME <- read_csv("data/MicrosoftEmotions.csv")
SB <- read_csv("data/SkybiometryEmotions.csv")
GE <- read_csv("SoftwareRequestScripts/GoogleClassifiedFaces.csv")
GF <- read_csv("data/GoogleFaces.csv")
#ALLmetaIMGnamed <- read.csv("ALLmetaIMGnamed.csv")

@@

@@

Connect face id to original Google set
```{r}
GEsub <- GE[,c(1, 10:13, 17:24)]

GE1 <- GEsub %>% 
  rowwise() %>%
  mutate(minX = pmin(cbind(boundingPoly.x1, boundingPoly.x4)), 
         maxX = pmin(cbind(boundingPoly.x2, boundingPoly.x3)),
         minY = pmin(cbind(boundingPoly.y1, boundingPoly.y2)), 
         maxY = pmin(cbind(boundingPoly.y3, boundingPoly.y4))) %>%
  ungroup()

GE1 <- GE1[,c(1:5, 14:17)]
```

Add meta data to Emotion results
```{r}
GE <- left_join(GF, GE1, by = c("file","minX","maxX","minY","maxY"))

@@

Create normalized SB values
```{r}
SB<-SB %>%
  rowwise %>% mutate(z = (anger.confidence+
               disgust.confidence+
               fear.confidence+
               happiness.confidence+
               neutral_mood.confidence+
               sadness.confidence+
               surprise.confidence))

@@

```{r}
Conf <- function(Emot){
ifelse(Emot=="VERY_UNLIKELY", 10,  
        ifelse(Emot == "UNLIKELY", 30, 
                ifelse(Emot == "POSSIBLE", 50, 
                ifelse(Emot == "LIKELY", 70, 
                ifelse(Emot == "VERY_LIKELY", 90, NA)))))
}

@@

```{r}

@@

Parallel coordinate plots
```{r}
#p1 <- ggparcoord(data = set1, columns = 2:9, groupColumn="file", order = "allClass")

#p2 <- ggparcoord(data = set2, columns = 2:9, groupColumn="file", order = "allClass")

#p3 <- ggparcoord(data = set3, columns = 2:9, groupColumn="file", order = "allClass")
```

Consider just players,
GEP: Microsoft's results, emotion data for only players
MEP: Skybiometry's results, emotion data for only players
SBP: Google's results, emotion data for only players
```{r}
GEP <- GE %>% filter(detect=="Player")
MEP <- ME %>% filter(detect=="Player")
SBP <- SB %>% filter(detect=="Player")

@@

```{r}

ggSBPne <- ggplot(SBP, aes(x=neutral))+geom_histogram(bins=15) +coord_cartesian(xlim = c(0, 1))
ggSBne <- ggplot(SB, aes(x=neutral))+geom_histogram(bins=15) +coord_cartesian(xlim = c(0, 1))

ggSBPan <- ggplot(SBP, aes(x=anger))+geom_histogram(bins=15) +coord_cartesian(xlim = c(0, 1))
ggSBPdi <- ggplot(SBP, aes(x=disgust))+geom_histogram(bins=15) +coord_cartesian(xlim = c(0, 1))
ggSBPfe <- ggplot(SBP, aes(x=fear))+geom_histogram(bins=15) +coord_cartesian(xlim = c(0, 1))
ggSBPha <- ggplot(SBP, aes(x=happiness))+geom_histogram(bins=15) +coord_cartesian(xlim = c(0, 1))
ggSBPsa <- ggplot(SBP, aes(x=sadness))+geom_histogram(bins=15) +coord_cartesian(xlim = c(0, 1))
ggSBPsu <- ggplot(SBP, aes(x=surprise))+geom_histogram(bins=15) +coord_cartesian(xlim = c(0, 1))

grid.arrange(ggSBPne,
             ggSBPan,
             ggSBPdi,
             ggSBPfe,
             ggSBPha,
             ggSBPsa,
             ggSBPsu, nrow=3)

@@

Microsoft Emotion plots
```{r}
ggMEPne<-ggplot(MEP, aes(x=neutral))+geom_histogram(bins=15) +coord_cartesian(xlim = c(0, 1))
ggMEPan<-ggplot(MEP, aes(x=anger))+geom_histogram(bins=15) +coord_cartesian(xlim = c(0, 1))
ggMEPdi<-ggplot(MEP, aes(x=disgust))+geom_histogram(bins=15) +coord_cartesian(xlim = c(0, 1))
ggMEPfe<-ggplot(MEP, aes(x=fear))+geom_histogram(bins=15) +coord_cartesian(xlim = c(0, 1))
ggMEPha<-ggplot(MEP, aes(x=happiness))+geom_histogram(bins=15) +coord_cartesian(xlim = c(0, 1))
ggMEPsa<-ggplot(MEP, aes(x=sadness))+geom_histogram(bins=15) +coord_cartesian(xlim = c(0, 1))
ggMEPsu<-ggplot(MEP, aes(x=surprise))+geom_histogram(bins=15) +coord_cartesian(xlim = c(0, 1))

@@

###
Join emotions for each face
```{r}
S1 <- select(SBPCL1, FileName = aname , SEmotion = Emotion)
S2 <- select(MEPCL1, FileName, MEmotion = Emotion)
S3 <- select(GEPCL1, FileName, GEmotion = Emotion)
J1 <- full_join(S1, S2, by = "FileName")
J2 <- full_join(J1, S3, by = "FileName")

@@

J2L<-J2 %>% 
  gather(key = Software, value = Emotion, SEmotion, MEmotion, GEmotion)

@@

SER<-read_csv("SampleEmotionResults.csv")

@@

Player Subsetting
```{r}
#Create column for Player Names
#GoogleFaces$PlayerName<-NA

@@

Player Emotion Tables

>>>>

```{r echo=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = F, warning = F, cache=T)

@@

```{r readdata}
#EmoM <-read_csv("data/EmotionsMerged.csv")
ME <- read_csv("data/MicrosoftEmotions.csv")
SB <- read_csv("data/SkybiometryEmotions.csv")
GE <- read_csv("data/GoogleFacesEmotions.csv")
GF <- read_csv("data/GoogleFaces.csv")
#ALLmetaIMGnamed <- read.csv("ALLmetaIMGnamed.csv")

@@

#Create column for Player Names
#GF$PlayerNumber<-NA

GF <- GF %>% rowwise %>%
  mutate(playerName = ifelse(PlayerNumber == 1, player1,
                                            ifelse(PlayerNumber == 2, player2,
                                                   ifelse(is.na(PlayerNumber), NA, NA))))

GE <- GE %>% rowwise %>%
  mutate(playerName = ifelse(PlayerNumber == 1, player1,
                                            ifelse(PlayerNumber == 2, player2,
                                                   ifelse(is.na(PlayerNumber), NA, NA))))

@@

Connect face id to original Google set
```{r googleSubset}
# GEsub <- GE[,c(1, 10:13, 17:24)]
# 
# GE1 <- GEsub %>% 
#   rowwise() %>%
#   mutate(minX = pmin(cbind(boundingPoly.x1, boundingPoly.x4)), 
#          maxX = pmin(cbind(boundingPoly.x2, boundingPoly.x3)),
#          minY = pmin(cbind(boundingPoly.y1, boundingPoly.y2)), 
#          maxY = pmin(cbind(boundingPoly.y3, boundingPoly.y4))) %>%
#   ungroup()
# 
# GE1 <- GE1[,c(1:5, 14:17)]
```

Add meta data to Emotion results
```{r mergeEmotMeta}
#GE <- left_join(GF, GE1, by = c("file","minX","maxX","minY","maxY"))

@@

Create normalized SB values
```{r normaliseSB}
SB<-SB %>%
  rowwise %>% mutate(z = (anger.confidence+
               disgust.confidence+
               fear.confidence+
               happiness.confidence+
               neutral_mood.confidence+
               sadness.confidence+
               surprise.confidence))

@@

```{r normaliseGE}
Conf <- function(Emot){
ifelse(Emot=="VERY_UNLIKELY", 10,  
        ifelse(Emot == "UNLIKELY", 30, 
                ifelse(Emot == "POSSIBLE", 50, 
                ifelse(Emot == "LIKELY", 70, 
                ifelse(Emot == "VERY_LIKELY", 90, NA)))))
}

@@

```{r TFemotions}

@@

Consider just players,
GEP: Microsoft's results, emotion data for only players
MEP: Skybiometry's results, emotion data for only players
SBP: Google's results, emotion data for only players
```{r playerSubset}
GEP <- GE %>% filter(detect=="Player")
MEP <- ME %>% filter(detect=="Player")
SBP <- SB %>% filter(detect=="Player")

@@

```{r SBhists}

ggSBPne <- ggplot(SBP, aes(x=neutral))+geom_histogram(binwidth=0.025) +coord_cartesian(xlim = c(0, 1), ylim = c(0,300))
ggSBPan <- ggplot(SBP, aes(x=anger))+geom_histogram(binwidth=0.025) +coord_cartesian(xlim = c(0, 1), ylim = c(0,300))
ggSBPdi <- ggplot(SBP, aes(x=disgust))+geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,300))
ggSBPfe <- ggplot(SBP, aes(x=fear))+geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,300))
ggSBPha <- ggplot(SBP, aes(x=happiness))+geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,300))
ggSBPsa <- ggplot(SBP, aes(x=sadness))+geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,300))
ggSBPsu <- ggplot(SBP, aes(x=surprise))+geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,300))

grid.arrange(ggSBPne,
             ggSBPan,
             ggSBPdi,
             ggSBPfe,
             ggSBPha,
             ggSBPsa,
             ggSBPsu, nrow=3)
```

@@

Microsoft Emotion plots
```{r}
ggMEPne<-ggplot(MEP, aes(x=neutral)) + geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,420))
ggMEPan<-ggplot(MEP, aes(x=anger)) + geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,420))
ggMEPdi<-ggplot(MEP, aes(x=disgust)) + geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,420))
ggMEPfe<-ggplot(MEP, aes(x=fear)) + geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,420))
ggMEPha<-ggplot(MEP, aes(x=happiness)) + geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,420))
ggMEPsa<-ggplot(MEP, aes(x=sadness)) + geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,420))
ggMEPsu<-ggplot(MEP, aes(x=surprise)) + geom_histogram(binwidth=0.055) +coord_cartesian(xlim = c(0, 1), ylim = c(0,420))

@@

###
Join emotions for each face
J2: Table of FileNames and associated dominant emotion
```{r}
S1 <- select(SBPCL1, FileName = aname , SEmotion = Emotion)
S2 <- select(MEPCL1, FileName, MEmotion = Emotion)
S3 <- select(GEPCL1, FileName, GEmotion = Emotion)
J1 <- full_join(S1, S2, by = "FileName")
J2 <- full_join(J1, S3, by = "FileName")

@@

J2L <- J2 %>% 
  gather(key = Software, value = Emotion, SEmotion, MEmotion, GEmotion)

@@

SER<-read_csv("Figures/SampleEmotionResults.csv")

@@

Player Subsetting
```{r DisplayFaces}

@@

Player Emotion Tables
Distribution of emotion values for particular emotions across all images of a player
```{r Playerhists}
ggplot(na.omit(SBP), aes(x=playerName))+geom_bar()+ theme(axis.text.x = element_text(angle = 20))

Name <- "GSimon"

  SBPplayer <- SBP %>% filter(playerName == Name)

  ggSBPan <- 
    ggplot(SBPplayer, aes(x = anger)) + ggtitle("Skybiometry") +
    geom_histogram(binwidth = 0.05) + coord_cartesian(xlim = c(0, 1))

  GEPplayer <- GEP %>% filter(playerName == Name)

  ggGEPan <-
    ggplot(GEPplayer, aes(x = anger)) +  ggtitle("Google") +
    geom_histogram(binwidth = 0.05) + coord_cartesian(xlim = c(0, 1))

  MEPplayer <- MEP %>% filter(playerName == Name)

  ggMEPan <-
    ggplot(MEPplayer, aes(x = anger)) +  ggtitle("Microsoft") +
    geom_histogram(binwidth = 0.05) + coord_cartesian(xlim = c(0, 1))

grid.arrange(ggMEPan,ggSBPan,ggGEPan, nrow = 3)

TB<- as.list(MEPplayer$FileName)
DisplayFaces(TB)
```
